---
title: "REPRODUCIBLE RESEARCH PROYECT 1"
author: "JBRA"
date: "20/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Data

Loading activity.csv

```{r loading}
y<-file("activity.csv")
dfactivity<-read.csv(y)
```

## Mean

```{r mean}
dias<-unique(dfactivity$date)
ld<-length(dias)
dfpasosdia<-data.frame(Dia=dias,Pasos=NA)
for (i in 1:ld){
  pdias<-subset(dfactivity, date==dias[i])
  pasosdia<-sum(pdias$steps, na.rm=TRUE)
  dfpasosdia[i,2]<-pasosdia
}
hist(dfpasosdia$Pasos)
prom<-mean(dfpasosdia$Pasos)
med<-median(dfpasosdia$Pasos)

```

The mean of the total number of steps taken per day is `r prom`.
The median of the total number of steps taken per day is `r med`.


## INTERVAL
```{r interval}
int<-unique(dfactivity$interval)
li<-length(int)
dfpasosint<-data.frame(Intervalo=int,PromedioPasos=NA)
for (i in 1:li){
  pint<-subset(dfactivity, interval==int[i])
  meanpasosint<-mean(pint$steps, na.rm=TRUE)
  dfpasosint[i,2]<-meanpasosint
}
mx<-max(dfpasosint)
plot(dfpasosint)
```
The maximum average number of steps was in the `r mx` interval.

## MISSIN DATA
```{r NA}
nas<-sum(is.na (dfactivity$steps))
rows<-nrow(dfactivity)
for (i in 1:rows){
  if (is.na(dfactivity[i,1])){
    x<-subset(dfpasosint, Intervalo==dfactivity[i,3])
    dfactivity[i,1]<-x$PromedioPasos
  }
}
dias<-unique(dfactivity$date)
ld<-length(dias)
dfpasosdia2<-data.frame(Dia=dias,Pasos=NA)
for (i in 1:ld){
  pdias<-subset(dfactivity, date==dias[i])
  pasosdia<-sum(pdias$steps, na.rm=TRUE)
  dfpasosdia2[i,2]<-pasosdia
}
hist(dfpasosdia2$Pasos)
prom2<-mean(dfpasosdia$Pasos)
med2<-median(dfpasosdia$Pasos)

```
The number of NA's in Steps is `r nas`.

The mean with missing values is `r prom` , and the mean without missig values is `r prom2`.
The median with missing values is `r med`, and the median without missig values is `r med2`.

The histogram with the missing values looks more as a normal distribution.

## WEEKENDS

```{r weekends}
dfactivity[,2]<-as.Date(dfactivity[,2])
dfdia<-(weekday=NA)
dfactivity<-cbind(dfactivity,dfdia)
rows<-nrow(dfactivity)
for (i in 1:rows){
  day<-weekdays(dfactivity[i,2])
  if (day=="sábado" || day=="domingo"){
    dfactivity[i,4]<-"Weekend"
  }else{
    dfactivity[i,4]<-"Weekday"
  }
}
dfweekday<-subset(dfactivity, dfactivity[,4]=="Weekday")
dfweekend<-subset(dfactivity, dfdia=="Weekend")
dfpasosintweekday<-data.frame(Int=int,PromedioPasos=NA)
dfpasosintweekend<-data.frame(Int=int,PromedioPasos=NA)
for (i in 1:li){
  pintweekday<-subset(dfweekday, interval==int[i])
  meanpasosintweekday<-mean(pintweekday$steps, na.rm=TRUE)
  dfpasosintweekday[i,2]<-meanpasosintweekday
  pintweekend<-subset(dfweekend, interval==int[i])
  meanpasosintweekend<-mean(pintweekend$steps, na.rm=TRUE)
  dfpasosintweekend[i,2]<-meanpasosintweekend
}
y<-c(0,220)
par(mfrow=c(2,1))
par(mar=c(2,2,2,2))
plot(dfpasosintweekday,main="WEEKDAY",ylim=y)
plot(dfpasosintweekend, main ="WEEKEND",ylim=y)

```